The zoon R package for reproducible and shareable species distribution modelling

### 2017-01-23 ms.Rmd
adding Dave Gavaghan's text edits

---
title: "The zoon R package for reproducible and shareable species distribution modelling"
author: 
  - Nick Golding$^1$, Tom A. August$^2$, Tim C.D. Lucas$^3$, David K. Gavaghan$^4$, Emiel Van Loon$^5$ & Greg McInerny$^6$
  - $^1$ School of BioSciences, University of Melbourne, Parkville VIC, Australia
  - $^2$ NERC Centre for Ecology & Hydrology, Crowmarsh Gifford, Maclean Building, Wallingford, OX10 8BB, UK
  - $^3$ Oxford Big Data Institute, Li Ka Shing Centre for Health Information and Discovery Nuffield Department of Medicine, University of Oxford, Oxford, U.K.
  - $^4$ [please fill in]
  - $^5$ [please fill in]
  - $^6$ [please fill in]
bibliography: zoon_app.bib
csl: mee.csl
output:
  pdf_document:
    fig_caption: yes
    includes:
      in_header: latex_preamble.tex
---

@@

For example, a fundamental dispute over the ability of SDMs to detect environmental associations [@Beale2008; @Araujo2009; @Beale2009] was left unresolved as only the original publication shared their analytical code [@Beale2008].
Similarly, in the past decade the SDM community has failed to carry out any large scale comparisons of SDM methods, still relying on the work of @Elith2006 to make decisions, despite the development of hundreds of new methods as well as improved evaluation procedures [@Roberts2016].
The community's inability to repeat this comprehensive analysis is due to both lack of access to comparable data and the difficulty in learning and applying the many different pieces of software for model fitting.

>>>>

---
title: "The zoon R package for reproducible and shareable species distribution modelling"
author: 
  - Nick Golding$^1$, Tom A. August$^2$, Tim C.D. Lucas$^3$, David J. Gavaghan$^4$, Emiel Van Loon$^5$ & Greg McInerny$^6$
  - $^1$ School of BioSciences, University of Melbourne, Parkville VIC, Australia
  - $^2$ NERC Centre for Ecology & Hydrology, Crowmarsh Gifford, Maclean Building, Wallingford, OX10 8BB, UK
  - $^3$ Oxford Big Data Institute, Li Ka Shing Centre for Health Information and Discovery Nuffield Department of Medicine, University of Oxford, Oxford, U.K.
  - $^4$ Department of Computer Science, University of Oxford, Oxford, UK
  - $^5$ [please fill in]
  - $^6$ [please fill in]
bibliography: zoon_app.bib
csl: mee.csl
output:
  pdf_document:
    fig_caption: yes
    includes:
      in_header: latex_preamble.tex
---

@@

For example, a fundamental dispute over the ability of SDMs to detect environmental associations [@Beale2008; @Araujo2009; @Beale2009] was left unresolved as only the original publication shared their analytical code [@Beale2008].
Similarly, in the past decade the SDM community has failed to carry out any large scale comparisons of SDM methods, still relying on the work of @Elith2006 to make decisions, despite the development of hundreds of new methods as well as improved evaluation procedures since the publication of that study [@Roberts2016].
The community's inability to repeat this comprehensive analysis is due to both lack of access to comparable data and the difficulty in learning and applying the many different pieces of software for model fitting.
